\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2019-11-25 submission/manuscript.tex
NC added to analysis

\subsection{Introduction}\label{introduction}

@@

\subsection{Materials and Methods}\label{materials-and-methods}

\subsubsection{Sampling}\label{sampling}

@@

\subsubsection{DNA Isolation, Illumina 16S rRNA Sequencing and Sequences
Analysis}\label{dna-isolation-illumina-16s-rrna-sequencing-and-sequences-analysis}

@@

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(5'-GTGYCAGCMGCCGCGGTAA-3') and 806R (5'-GGACTACNVGGGTWTCTAAT-3')
primers from the Earth Microbiome Project
(\url{http://press.igsb.anl.gov/earthmicrobiome/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso \emph{et al.}, 2012;
Apprill \emph{et al.}, 2015; Parada \emph{et al.}, 2016). These primers
contained on their 5' end a tagged sequence. Each sample was amplified
in four parallel 25 \si{\ul} reactions of which each contained: 1 × Q5
Reaction Buffer , 0.2 \si{\milli\Molar} of dNTPmix, 0.7 \si{\mg\per\ml}
BSA (Bovine Serum Albumin), 0.2 \si{\micro\Molar} of forward and reverse
primers, 0.5 U of Q5 High-Fidelity DNA Polymerase (New England Biolabs,
USA) and 5 \si{\ng} of DNA template. Cycling conditions were: initial
denaturation at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of
denaturation at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing, at IMGM the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a postive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. The sequences obtained in this study have been submitted to the
European Nucleotide Archive (ENA) under accession numbers ??????????.

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0)(Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommandations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
132; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplsts by
mothur were exported, aligned using SILVA incremental aligner (SINA,
version 1.6.0) (Pruesse \emph{et al.}, 2012) against the same SILVA SSU
Ref NR 99 database (release 132) and imported into ARB (version 6.0.6)
(Ludwig \emph{et al.}, 2004) for further phylogentic analysis using the
same database. Reference sequences close to imported were selected and
used to calculate a phylogentic tree using the Maximum Likelihood
algorithm RAxML (version 7.0.3) with 1000 tree replicates (Stamatakis,
2006). Imported partial chloroplast sequences were added to the tree
using the maximum parsimony criteria and not allowing changes to tree
topology. Pipeline data processing and visualizaion was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.2.1)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2019a, 2019b; Xie \emph{et al.}, 2018; Zhu, 2019; Allaire \emph{et
al.}, 2019). The detailed analysis procedure including the R Markdown
file for this paper are available as a GitHub repository (??????).

\subsubsection{Protein Isolation and
Metaproteomics}\label{protein-isolation-and-metaproteomics}

@@

\subsubsection{Confocal Microscopy}\label{confocal-microscopy}

\subsection{Results and Discussion}\label{results-and-discussion}

\subsection{Conclusions}\label{conclusions}

\subsection{Materials and Methods}\label{materials-and-methods-1}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-Allaire2019}{}
Allaire, J.J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., et al. (2019) rmarkdown: Dynamic Documents for R.

\hypertarget{ref-Amann1995}{}
Amann, R.I., Ludwig, W., and Schleifer, K.H. (1995) Phylogenetic
identification and in situ detection of individual microbial cells
without cultivation. \emph{Microbiological reviews} \textbf{59}:
143--169.

\hypertarget{ref-Andersson2010}{}
Andersson, A.F., Riemann, L., and Bertilsson, S. (2010) Pyrosequencing
reveals contrasting seasonal dynamics of taxa within Baltic Sea
bacterioplankton communities. \emph{The ISME journal} \textbf{4}:
171--181.

\hypertarget{ref-Apprill2015}{}
Apprill, A., McNally, S., Parsons, R., and Weber, L. (2015) Minor
revision to V4 region SSU rRNA 806R gene primer greatly increases
detection of SAR11 bacterioplankton. \emph{Aquatic Microbial Ecology}
\textbf{75}: 129--137.

\hypertarget{ref-Burke2009}{}
Burke, C., Kjelleberg, S., and Thomas, T. (2009) Selective extraction of
bacterial DNA from the surfaces of macroalgae. \emph{Applied and
environmental microbiology} \textbf{75}: 252--256.

\hypertarget{ref-Burke2011a}{}
Burke, C., Steinberg, P., Rusch, D., Kjelleberg, S., and Thomas, T.
(2011a) Bacterial community assembly based on functional genes rather
than species. \emph{Proceedings of the National Academy of Sciences of
the United States of America} \textbf{108}: 14288--14293.

\hypertarget{ref-Burke2011b}{}
Burke, C., Thomas, T., Lewis, M., Steinberg, P., and Kjelleberg, S.
(2011b) Composition, uniqueness and variability of the epiphytic
bacterial community of the green alga Ulva australis. \emph{The ISME
journal} \textbf{5}: 590--600.

\hypertarget{ref-Cai2014}{}
Cai, X., Gao, G., Yang, J., Tang, X., Dai, J., Chen, D., and Song, Y.
(2014) An ultrasonic method for separation of epiphytic microbes from
freshwater submerged macrophytes. \emph{Journal of basic microbiology}
\textbf{54}: 758--761.

\hypertarget{ref-Caporaso2012}{}
Caporaso, J.G., Lauber, C.L., Walters, W.A., Berg-Lyons, D., Huntley,
J., Fierer, N., et al. (2012) Ultra-high-throughput microbial community
analysis on the Illumina HiSeq and MiSeq platforms. \emph{The ISME
Journal} \textbf{6}: 1621--1624.

\hypertarget{ref-Chourey2010}{}
Chourey, K., Jansson, J., VerBerkmoes, N., Shah, M., Chavarria, K.L.,
Tom, L.M., et al. (2010) Direct Cellular Lysis/Protein Extraction
Protocol for Soil Metaproteomics. \emph{Journal of Proteome Research}
\textbf{9}: 6615--6622.

\hypertarget{ref-Egan2013}{}
Egan, S., Harder, T., Burke, C., Steinberg, P., Kjelleberg, S., and
Thomas, T. (2013) The seaweed holobiont: understanding seaweed-bacteria
interactions. \emph{FEMS microbiology reviews} \textbf{37}: 462--476.

\hypertarget{ref-Gilbert2009}{}
Gilbert, J.A., Field, D., Swift, P., Newbold, L., Oliver, A., Smyth, T.,
et al. (2009) The seasonal structure of microbial communities in the
Western English Channel. \emph{Environmental Microbiology} \textbf{11}:
3132--3139.

\hypertarget{ref-Gross2003}{}
Gross, E.M., Feldbaum, C., and Graf, A. (2003) Epiphyte biomass and
elemental composition on submersed macrophytes in shallow eutrophic
lakes. \emph{Hydrobiologia} \textbf{506-509}: 559--565.

\hypertarget{ref-Hultman2015}{}
Hultman, J., Waldrop, M.P., Mackelprang, R., David, M.M., McFarland, J.,
Blazewicz, S.J., et al. (2015) Multi-omics of permafrost, active layer
and thermokarst bog soil microbiomes. \emph{Nature} \textbf{521}:
208--212.

\hypertarget{ref-Jiang2015}{}
Jiang, Y.-F., Ling, J., Dong, J.-D., Chen, B., Zhang, Y.-Y., Zhang,
Y.-Z., and Wang, Y.-S. (2015) Illumina-based analysis the microbial
diversity associated with Thalassia hemprichii in Xincun Bay, South
China Sea. \emph{Ecotoxicology (London, England)} \textbf{24}: 1548--56.

\hypertarget{ref-Kozich2013}{}
Kozich, J.J., Westcott, S.L., Baxter, N.T., Highlander, S.K., and
Schloss, P.D. (2013) Development of a dual-index sequencing strategy and
curation pipeline for analyzing amplicon sequence data on the MiSeq
Illumina sequencing platform. \emph{Applied and environmental
microbiology} \textbf{79}: 5112--5120.

\hypertarget{ref-Longford2007}{}
Longford, S., Tujula, N., Crocetti, G., Holmes, A., Holmström, C.,
Kjelleberg, S., et al. (2007) Comparisons of diversity of bacterial
communities associated with three sessile marine eukaryotes.
\emph{Aquatic Microbial Ecology} \textbf{48}: 217--229.

\hypertarget{ref-Ludwig2004}{}
Ludwig, W., Strunk, O., Westram, R., Richter, L., Meier, H., Yadhukumar,
et al. (2004) ARB: a software environment for sequence data.
\emph{Nucleic Acids Research} \textbf{32}: 1363--1371.

\hypertarget{ref-Massana1997}{}
Massana, R., Murray, A.E., Preston, C.M., and DeLong, E.F. (1997)
Vertical distribution and phylogenetic characterization of marine
planktonic Archaea in the Santa Barbara Channel. \emph{Applied and
environmental microbiology} \textbf{63}: 50--56.

\hypertarget{ref-Noges2010}{}
Nõges, T., Luup, H., and Feldmann, T. (2010) Primary production of
aquatic macrophytes and their epiphytes in two shallow lakes (Peipsi and
Võrtsjärv) in Estonia. \emph{Aquatic Ecology} \textbf{44}: 83--92.

\hypertarget{ref-Parada2016}{}
Parada, A.E., Needham, D.M., and Fuhrman, J.A. (2016) Every base
matters: assessing small subunit rRNA primers for marine microbiomes
with mock communities, time series and global field samples.
\emph{Environmental Microbiology} \textbf{18}: 1403--1414.

\hypertarget{ref-Pruesse2012}{}
Pruesse, E., Peplies, J., and Glöckner, F.O. (2012) SINA: accurate
high-throughput multiple sequence alignment of ribosomal RNA genes.
\emph{Bioinformatics (Oxford, England)} \textbf{28}: 1823--1829.

\hypertarget{ref-Quast2013}{}
Quast, C., Pruesse, E., Yilmaz, P., Gerken, J., Schweer, T., Yarza, P.,
et al. (2013) The SILVA ribosomal RNA gene database project: improved
data processing and web-based tools. \emph{Nucleic acids research}
\textbf{41}: D590--6.

\hypertarget{ref-RCoreTeam2019}{}
R Core Team (2019) R: A Language and Environment for Statistical
Computing, Vienna, Austria: R Foundation for Statistical Computing.

\hypertarget{ref-Richter-Heitmann2016}{}
Richter-Heitmann, T., Eickhorst, T., Knauth, S., Friedrich, M.W., and
Schmidt, H. (2016) Evaluation of Strategies to Separate Root-Associated
Microbial Communities: A Crucial Choice in Rhizobiome Research.
\emph{Frontiers in Microbiology} \textbf{7}: 773.

\hypertarget{ref-Schloss2009}{}
Schloss, P.D., Westcott, S.L., Ryabin, T., Hall, J.R., Hartmann, M.,
Hollister, E.B., et al. (2009) Introducing mothur: open-source,
platform-independent, community-supported software for describing and
comparing microbial communities. \emph{Applied and environmental
microbiology} \textbf{75}: 7537--7541.

\hypertarget{ref-Stamatakis2006}{}
Stamatakis, A. (2006) RAxML-VI-HPC: maximum likelihood-based
phylogenetic analyses with thousands of taxa and mixed models.
\emph{Bioinformatics} \textbf{22}: 2688--2690.

\hypertarget{ref-Staufenberger2008}{}
Staufenberger, T., Thiel, V., Wiese, J., and Imhoff, J.F. (2008)
Phylogenetic analysis of bacteria associated with Laminaria saccharina.
\emph{FEMS Microbiology Ecology} \textbf{64}: 65--77.

\hypertarget{ref-Su2012}{}
Su, C., Lei, L., Duan, Y., Zhang, K.-Q., and Yang, J. (2012)
Culture-independent methods for studying environmental microorganisms:
methods, application, and perspective. \emph{Applied microbiology and
biotechnology} \textbf{93}: 993--1003.

\hypertarget{ref-Uku2007}{}
Uku, J., Björk, M., Bergman, B., and Díez, B. (2007) Characterization
and comparison of prokaryotic epiphytes associated with three East
African seagrasses. \emph{Journal of Phycology} \textbf{43}: 768--779.

\hypertarget{ref-Weidner1996}{}
Weidner, S., Arnold, W., and Puhler, A. (1996) Diversity of uncultured
microorganisms associated with the seagrass Halophila stipulacea
estimated by restriction fragment length polymorphism analysis of
PCR-amplified 16S rRNA genes. \emph{Applied and environmental
microbiology} \textbf{62}: 766--771.

\hypertarget{ref-Wickham2019}{}
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.D., François,
R., et al. (2019) Welcome to the tidyverse. \emph{Journal of Open Source
Software} \textbf{4}: 1686.

\hypertarget{ref-Xie2015}{}
Xie, Y. (2015) Dynamic Documents with \{R\} and knitr, 2nd ed. Boca
Raton, Florida: Chapman; Hall/CRC.

\hypertarget{ref-Xie2014}{}
Xie, Y. (2014) knitr: A Comprehensive Tool for Reproducible Research in
\{R\}. In, Stodden,V., Leisch,F., and Peng,R.D. (eds),
\emph{Implementing reproducible computational research}. Chapman;
Hall/CRC.

\hypertarget{ref-Xie2019a}{}
Xie, Y. (2019a) knitr: A General-Purpose Package for Dynamic Report
Generation in R.

\hypertarget{ref-Xie2019}{}
Xie, Y. (2019b) tinytex: Helper Functions to Install and Maintain 'TeX
Live', and Compile 'LaTeX' Documents.

\hypertarget{ref-Xie2018}{}
Xie, Y., Allaire, J.J., and Grolemund, G. (2018) R Markdown: The
Definitive Guide, Boca Raton, Florida: Chapman; Hall/CRC.

\hypertarget{ref-Yilmaz2014}{}
Yilmaz, P., Parfrey, L.W., Yarza, P., Gerken, J., Pruesse, E., Quast,
C., et al. (2014) The SILVA and ``All-species Living Tree Project
(LTP)'' taxonomic frameworks. \emph{Nucleic acids research} \textbf{42}:
D643--8.

\hypertarget{ref-Zhu2019}{}
Zhu, H. (2019) kableExtra: Construct Complex Table with 'kable' and Pipe
Syntax.

>>>>

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

\hypertarget{sampling}{%
\subsubsection{Sampling}\label{sampling}}

@@

\hypertarget{dna-isolation-illumina-16s-rrna-sequencing-and-sequences-analysis}{%
\subsubsection{DNA Isolation, Illumina 16S rRNA Sequencing and Sequences
Analysis}\label{dna-isolation-illumina-16s-rrna-sequencing-and-sequences-analysis}}

@@

An aliquot of isolated DNA was treated with RNase A (final concentration
200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA
concentration was determined using the Quant-iT PicoGreen dsDNA Assay
Kit (Invitrogen, USA) according to the manufacturer's instructions and
diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was
amplified using a two-step PCR procedure. In the first PCR the 515F
(5'-GTGYCAGCMGCCGCGGTAA-3') and 806R (5'-GGACTACNVGGGTWTCTAAT-3')
primers from the Earth Microbiome Project
(\url{http://press.igsb.anl.gov/earthmicrobiome/protocols-and-standards/16s/})
were used to amplify the target region (Caporaso \emph{et al.}, 2012;
Apprill \emph{et al.}, 2015; Parada \emph{et al.}, 2016). These primers
contained on their 5' end a tagged sequence. Each sample was amplified
in four parallel 25 \si{\ul} reactions of which each contained: 1 × Q5
Reaction Buffer , 0.2 \si{\milli\Molar} of dNTPmix, 0.7 \si{\mg\per\ml}
BSA (Bovine Serum Albumin), 0.2 \si{\micro\Molar} of forward and reverse
primers, 0.5 U of Q5 High-Fidelity DNA Polymerase (New England Biolabs,
USA) and 5 \si{\ng} of DNA template. Cycling conditions were: initial
denaturation at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of
denaturation at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50
\si{\degreeCelsius} for 60 \si{\s} and elongation at 72
\si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at
72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions
volumes were pooled and PCR products were purified using the GeneJET PCR
Purification Kit (Thermo Fisher Scientific, USA) according to the
manufacturer's instructions and following the protocol that included
isopropanol addition for better small DNA fragment yield. The column was
eluted in 30 \si{\ul} of deionized water. Purified PCR products were
sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories,
Martinsried, Germany. Before sequencing, at IMGM the second PCR
amplification of the two-step PCR procedure was performed using primers
targeting the tagged region incorporated in the first PCR. In addition,
these primers contained adapter and sample-specific index sequences. The
second PCR was carried out for 8 cycles. Beside samples, a positive and
negative control were sequenced. A negative control was comprised of
four parallel PCR reactions without DNA template, while for a postive
control a mock community composed of evenly mixed DNA material
originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was
used. The sequences obtained in this study have been submitted to the
European Nucleotide Archive (ENA) under accession numbers ?????.

\begin{verbatim}
## Parsed with column specification:
## cols(
##   .default = col_double(),
##   query = col_character(),
##   reference = col_character()
## )
\end{verbatim}

\begin{verbatim}
## See spec(...) for full column specifications.
\end{verbatim}

\begin{verbatim}
## Parsed with column specification:
## cols(
##   taxlevel = col_double(),
##   rankID = col_character(),
##   taxon = col_character(),
##   daughterlevels = col_double(),
##   total = col_double(),
##   `40` = col_double(),
##   `41` = col_double(),
##   `42` = col_double(),
##   `43` = col_double(),
##   `61` = col_double(),
##   `62` = col_double(),
##   `63` = col_double(),
##   ATCC_1 = col_double(),
##   NC_1 = col_double()
## )
\end{verbatim}

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommandations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
132; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplsts by
mothur were exported, aligned using SILVA incremental aligner (SINA,
version 1.6.0) (Pruesse \emph{et al.}, 2012) against the same SILVA SSU
Ref NR 99 database (release 132) and imported into ARB (version 6.0.6)
(Ludwig \emph{et al.}, 2004) for further phylogentic analysis using the
same database. Reference sequences close to imported ones were selected
and used to calculate a phylogentic tree using the Maximum Likelihood
algorithm RAxML (version 7.0.3) with 1000 tree replicates (Stamatakis,
2006). Imported partial chloroplast sequences were added to the tree
using the maximum parsimony criteria and not allowing changes to tree
topology. Pipeline data processing and visualizaion was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.2.1)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2019a, 2019b; Xie \emph{et al.}, 2018; Zhu, 2019; Allaire \emph{et
al.}, 2019). The detailed analysis procedure including the R Markdown
file for this paper are available as a GitHub repository (?????). Based
on the ATCC MSA-1002 mock community included in the analysis a
sequencing error rate of 0.009 \si{\percent} was detemined that is in
line with previously reported values for next-generation sequencing data
(Kozich \emph{et al.}, 2013; Schloss \emph{et al.}, 2016). In addition,
the negative control processed together with the samples yielded only
44,050 sequences.

\hypertarget{protein-isolation-and-metaproteomics}{%
\subsubsection{Protein Isolation and
Metaproteomics}\label{protein-isolation-and-metaproteomics}}

@@

\hypertarget{confocal-microscopy}{%
\subsubsection{Confocal Microscopy}\label{confocal-microscopy}}

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

\hypertarget{materials-and-methods-1}{%
\subsection{Materials and Methods}\label{materials-and-methods-1}}

@@

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire2019}{}%
Allaire, J.J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., et al. (2019) rmarkdown: Dynamic Documents for R.

\leavevmode\hypertarget{ref-Amann1995}{}%
Amann, R.I., Ludwig, W., and Schleifer, K.H. (1995) Phylogenetic
identification and in situ detection of individual microbial cells
without cultivation. \emph{Microbiological reviews} \textbf{59}:
143--169.

\leavevmode\hypertarget{ref-Andersson2010}{}%
Andersson, A.F., Riemann, L., and Bertilsson, S. (2010) Pyrosequencing
reveals contrasting seasonal dynamics of taxa within Baltic Sea
bacterioplankton communities. \emph{The ISME journal} \textbf{4}:
171--181.

\leavevmode\hypertarget{ref-Apprill2015}{}%
Apprill, A., McNally, S., Parsons, R., and Weber, L. (2015) Minor
revision to V4 region SSU rRNA 806R gene primer greatly increases
detection of SAR11 bacterioplankton. \emph{Aquatic Microbial Ecology}
\textbf{75}: 129--137.

\leavevmode\hypertarget{ref-Burke2009}{}%
Burke, C., Kjelleberg, S., and Thomas, T. (2009) Selective extraction of
bacterial DNA from the surfaces of macroalgae. \emph{Applied and
environmental microbiology} \textbf{75}: 252--256.

\leavevmode\hypertarget{ref-Burke2011a}{}%
Burke, C., Steinberg, P., Rusch, D., Kjelleberg, S., and Thomas, T.
(2011a) Bacterial community assembly based on functional genes rather
than species. \emph{Proceedings of the National Academy of Sciences of
the United States of America} \textbf{108}: 14288--14293.

\leavevmode\hypertarget{ref-Burke2011b}{}%
Burke, C., Thomas, T., Lewis, M., Steinberg, P., and Kjelleberg, S.
(2011b) Composition, uniqueness and variability of the epiphytic
bacterial community of the green alga Ulva australis. \emph{The ISME
journal} \textbf{5}: 590--600.

\leavevmode\hypertarget{ref-Cai2014}{}%
Cai, X., Gao, G., Yang, J., Tang, X., Dai, J., Chen, D., and Song, Y.
(2014) An ultrasonic method for separation of epiphytic microbes from
freshwater submerged macrophytes. \emph{Journal of basic microbiology}
\textbf{54}: 758--761.

\leavevmode\hypertarget{ref-Caporaso2012}{}%
Caporaso, J.G., Lauber, C.L., Walters, W.A., Berg-Lyons, D., Huntley,
J., Fierer, N., et al. (2012) Ultra-high-throughput microbial community
analysis on the Illumina HiSeq and MiSeq platforms. \emph{The ISME
Journal} \textbf{6}: 1621--1624.

\leavevmode\hypertarget{ref-Chourey2010}{}%
Chourey, K., Jansson, J., VerBerkmoes, N., Shah, M., Chavarria, K.L.,
Tom, L.M., et al. (2010) Direct Cellular Lysis/Protein Extraction
Protocol for Soil Metaproteomics. \emph{Journal of Proteome Research}
\textbf{9}: 6615--6622.

\leavevmode\hypertarget{ref-Egan2013}{}%
Egan, S., Harder, T., Burke, C., Steinberg, P., Kjelleberg, S., and
Thomas, T. (2013) The seaweed holobiont: understanding seaweed-bacteria
interactions. \emph{FEMS microbiology reviews} \textbf{37}: 462--476.

\leavevmode\hypertarget{ref-Gilbert2009}{}%
Gilbert, J.A., Field, D., Swift, P., Newbold, L., Oliver, A., Smyth, T.,
et al. (2009) The seasonal structure of microbial communities in the
Western English Channel. \emph{Environmental Microbiology} \textbf{11}:
3132--3139.

\leavevmode\hypertarget{ref-Gross2003}{}%
Gross, E.M., Feldbaum, C., and Graf, A. (2003) Epiphyte biomass and
elemental composition on submersed macrophytes in shallow eutrophic
lakes. \emph{Hydrobiologia} \textbf{506-509}: 559--565.

\leavevmode\hypertarget{ref-Hultman2015}{}%
Hultman, J., Waldrop, M.P., Mackelprang, R., David, M.M., McFarland, J.,
Blazewicz, S.J., et al. (2015) Multi-omics of permafrost, active layer
and thermokarst bog soil microbiomes. \emph{Nature} \textbf{521}:
208--212.

\leavevmode\hypertarget{ref-Jiang2015}{}%
Jiang, Y.-F., Ling, J., Dong, J.-D., Chen, B., Zhang, Y.-Y., Zhang,
Y.-Z., and Wang, Y.-S. (2015) Illumina-based analysis the microbial
diversity associated with Thalassia hemprichii in Xincun Bay, South
China Sea. \emph{Ecotoxicology (London, England)} \textbf{24}: 1548--56.

\leavevmode\hypertarget{ref-Kozich2013}{}%
Kozich, J.J., Westcott, S.L., Baxter, N.T., Highlander, S.K., and
Schloss, P.D. (2013) Development of a dual-index sequencing strategy and
curation pipeline for analyzing amplicon sequence data on the MiSeq
Illumina sequencing platform. \emph{Applied and environmental
microbiology} \textbf{79}: 5112--5120.

\leavevmode\hypertarget{ref-Longford2007}{}%
Longford, S., Tujula, N., Crocetti, G., Holmes, A., Holmström, C.,
Kjelleberg, S., et al. (2007) Comparisons of diversity of bacterial
communities associated with three sessile marine eukaryotes.
\emph{Aquatic Microbial Ecology} \textbf{48}: 217--229.

\leavevmode\hypertarget{ref-Ludwig2004}{}%
Ludwig, W., Strunk, O., Westram, R., Richter, L., Meier, H., Yadhukumar,
et al. (2004) ARB: a software environment for sequence data.
\emph{Nucleic Acids Research} \textbf{32}: 1363--1371.

\leavevmode\hypertarget{ref-Massana1997}{}%
Massana, R., Murray, A.E., Preston, C.M., and DeLong, E.F. (1997)
Vertical distribution and phylogenetic characterization of marine
planktonic Archaea in the Santa Barbara Channel. \emph{Applied and
environmental microbiology} \textbf{63}: 50--56.

\leavevmode\hypertarget{ref-Noges2010}{}%
Nõges, T., Luup, H., and Feldmann, T. (2010) Primary production of
aquatic macrophytes and their epiphytes in two shallow lakes (Peipsi and
Võrtsjärv) in Estonia. \emph{Aquatic Ecology} \textbf{44}: 83--92.

\leavevmode\hypertarget{ref-Parada2016}{}%
Parada, A.E., Needham, D.M., and Fuhrman, J.A. (2016) Every base
matters: assessing small subunit rRNA primers for marine microbiomes
with mock communities, time series and global field samples.
\emph{Environmental Microbiology} \textbf{18}: 1403--1414.

\leavevmode\hypertarget{ref-Pruesse2012}{}%
Pruesse, E., Peplies, J., and Glöckner, F.O. (2012) SINA: accurate
high-throughput multiple sequence alignment of ribosomal RNA genes.
\emph{Bioinformatics (Oxford, England)} \textbf{28}: 1823--1829.

\leavevmode\hypertarget{ref-Quast2013}{}%
Quast, C., Pruesse, E., Yilmaz, P., Gerken, J., Schweer, T., Yarza, P.,
et al. (2013) The SILVA ribosomal RNA gene database project: improved
data processing and web-based tools. \emph{Nucleic acids research}
\textbf{41}: D590--6.

\leavevmode\hypertarget{ref-RCoreTeam2019}{}%
R Core Team (2019) R: A Language and Environment for Statistical
Computing, Vienna, Austria: R Foundation for Statistical Computing.

\leavevmode\hypertarget{ref-Richter-Heitmann2016}{}%
Richter-Heitmann, T., Eickhorst, T., Knauth, S., Friedrich, M.W., and
Schmidt, H. (2016) Evaluation of Strategies to Separate Root-Associated
Microbial Communities: A Crucial Choice in Rhizobiome Research.
\emph{Frontiers in Microbiology} \textbf{7}: 773.

\leavevmode\hypertarget{ref-Schloss2016}{}%
Schloss, P.D., Girard, R.A., Martin, T., Edwards, J., and Thrash, J.C.
(2016) Status of the Archaeal and Bacterial Census: an Update.
\emph{mBio} \textbf{7}: e00201--16.

\leavevmode\hypertarget{ref-Schloss2009}{}%
Schloss, P.D., Westcott, S.L., Ryabin, T., Hall, J.R., Hartmann, M.,
Hollister, E.B., et al. (2009) Introducing mothur: open-source,
platform-independent, community-supported software for describing and
comparing microbial communities. \emph{Applied and environmental
microbiology} \textbf{75}: 7537--7541.

\leavevmode\hypertarget{ref-Stamatakis2006}{}%
Stamatakis, A. (2006) RAxML-VI-HPC: maximum likelihood-based
phylogenetic analyses with thousands of taxa and mixed models.
\emph{Bioinformatics} \textbf{22}: 2688--2690.

\leavevmode\hypertarget{ref-Staufenberger2008}{}%
Staufenberger, T., Thiel, V., Wiese, J., and Imhoff, J.F. (2008)
Phylogenetic analysis of bacteria associated with Laminaria saccharina.
\emph{FEMS Microbiology Ecology} \textbf{64}: 65--77.

\leavevmode\hypertarget{ref-Su2012}{}%
Su, C., Lei, L., Duan, Y., Zhang, K.-Q., and Yang, J. (2012)
Culture-independent methods for studying environmental microorganisms:
methods, application, and perspective. \emph{Applied microbiology and
biotechnology} \textbf{93}: 993--1003.

\leavevmode\hypertarget{ref-Uku2007}{}%
Uku, J., Björk, M., Bergman, B., and Díez, B. (2007) Characterization
and comparison of prokaryotic epiphytes associated with three East
African seagrasses. \emph{Journal of Phycology} \textbf{43}: 768--779.

\leavevmode\hypertarget{ref-Weidner1996}{}%
Weidner, S., Arnold, W., and Puhler, A. (1996) Diversity of uncultured
microorganisms associated with the seagrass Halophila stipulacea
estimated by restriction fragment length polymorphism analysis of
PCR-amplified 16S rRNA genes. \emph{Applied and environmental
microbiology} \textbf{62}: 766--771.

\leavevmode\hypertarget{ref-Wickham2019}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.D., François,
R., et al. (2019) Welcome to the tidyverse. \emph{Journal of Open Source
Software} \textbf{4}: 1686.

\leavevmode\hypertarget{ref-Xie2015}{}%
Xie, Y. (2015) Dynamic Documents with \{R\} and knitr, 2nd ed. Boca
Raton, Florida: Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Xie2014}{}%
Xie, Y. (2014) knitr: A Comprehensive Tool for Reproducible Research in
\{R\}. In, Stodden,V., Leisch,F., and Peng,R.D. (eds),
\emph{Implementing reproducible computational research}. Chapman;
Hall/CRC.

\leavevmode\hypertarget{ref-Xie2019a}{}%
Xie, Y. (2019a) knitr: A General-Purpose Package for Dynamic Report
Generation in R.

\leavevmode\hypertarget{ref-Xie2019}{}%
Xie, Y. (2019b) tinytex: Helper Functions to Install and Maintain 'TeX
Live', and Compile 'LaTeX' Documents.

\leavevmode\hypertarget{ref-Xie2018}{}%
Xie, Y., Allaire, J.J., and Grolemund, G. (2018) R Markdown: The
Definitive Guide, Boca Raton, Florida: Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Yilmaz2014}{}%
Yilmaz, P., Parfrey, L.W., Yarza, P., Gerken, J., Pruesse, E., Quast,
C., et al. (2014) The SILVA and "All-species Living Tree Project (LTP)"
taxonomic frameworks. \emph{Nucleic acids research} \textbf{42}:
D643--8.

\leavevmode\hypertarget{ref-Zhu2019}{}%
Zhu, H. (2019) kableExtra: Construct Complex Table with 'kable' and Pipe
Syntax.
